Dynastic Extinctions and Urban Economic Development: \\Evidence from the Holy Roman Empire\footnote{I thank Davide Cantoni, Matthias Weigand, and my RA colleagues at the Chair of Economic History for helpful comments and feedback.}

### 2023-06-22 paper/output/regressions/SW22_replication_100y.tex
#28 round results to two decimals

\begin{table}[htbp]
   \caption{\label{tab:SW22_replication_100y} Dynamic effects of switching}
   \centering
   \begin{tabular}{lcccc}
      \tabularnewline \midrule \midrule
      Dependent Variables:           & All construction & State      & Private       & Public goods\\  
      Model:                         & (1)              & (2)        & (3)           & (4)\\  
      \midrule
      \emph{Variables}\\
      Treat $\times$ Period $=$ 0    & 0.02             & -0.03      & 0.0006        & -0.04$^{**}$\\   
                                     & (0.02)           & (0.03)     & (0.02)        & (0.02)\\   
      Treat $\times$ Period $=$ 100  & 0.09$^{***}$     & 0.02       & 0.01          & -0.008\\   
                                     & (0.03)           & (0.03)     & (0.03)        & (0.03)\\   
      Treat $\times$ Period $=$ 200  & 0.08$^{***}$     & -0.02      & -0.10$^{***}$ & -0.06$^{*}$\\   
                                     & (0.03)           & (0.04)     & (0.03)        & (0.04)\\   
      Switching indicator            & 0.02             & 0.06$^{*}$ & 0.009         & -0.02\\   
                                     & (0.03)           & (0.03)     & (0.02)        & (0.03)\\   
      \midrule
      \emph{Fixed-effects}\\
      City                           & Yes              & Yes        & Yes           & Yes\\  
      Period                         & Yes              & Yes        & Yes           & Yes\\  
      \midrule
      \emph{Fit statistics}\\
      Observations                   & 2,955            & 2,955      & 2,955         & 2,955\\  
      R$^2$                          & 0.4303           & 0.4530     & 0.4832        & 0.4499\\  
      Within R$^2$                   & 0.0048           & 0.0047     & 0.0064        & 0.0027\\  
      \midrule \midrule

>>>>

\begin{table}[htbp]
   \caption{\label{tab:SW22_replication_100y} Dynamic effects of switching}
   \centering
   \begin{tabular}{lcccc}
      \tabularnewline \midrule \midrule
      Dependent Variables:           & All construction & State      & Private       & Public goods\\  
      Model:                         & (1)              & (2)        & (3)           & (4)\\  
      \midrule
      \emph{Variables}\\
      Treat $\times$ Period $=$ 0    & 0.02             & -0.03      & 0.00          & -0.04$^{**}$\\   
                                     & (0.02)           & (0.02)     & (0.02)        & (0.02)\\   
      Treat $\times$ Period $=$ 100  & 0.09$^{***}$     & 0.02       & 0.01          & -0.01\\   
                                     & (0.03)           & (0.03)     & (0.03)        & (0.03)\\   
      Treat $\times$ Period $=$ 200  & 0.08$^{***}$     & -0.02      & -0.10$^{***}$ & -0.06$^{*}$\\   
                                     & (0.03)           & (0.04)     & (0.03)        & (0.04)\\   
      Switching indicator            & 0.02             & 0.06$^{*}$ & 0.01          & -0.02\\   
                                     & (0.03)           & (0.03)     & (0.02)        & (0.02)\\   
      \midrule
      \emph{Fixed-effects}\\
      City                           & Yes              & Yes        & Yes           & Yes\\  
      Period                         & Yes              & Yes        & Yes           & Yes\\  
      \midrule
      \emph{Fit statistics}\\
      Observations                   & 2,955            & 2,955      & 2,955         & 2,955\\  
      R$^2$                          & 0.4303           & 0.4530     & 0.4832        & 0.4499\\  
      Within R$^2$                   & 0.0048           & 0.0047     & 0.0064        & 0.0027\\  
      \midrule \midrule

### 2023-06-22 paper/output/regressions/window_100y.tex
#28 round results to two decimals

\begin{table}[htbp]
   \caption{\label{tab:window_100y} Differences in trends after switching, by switch type}
   \centering
   \begin{tabular}{lcccc}
      \tabularnewline \midrule \midrule
      Dependent Variables:                       & All construction & State       & Private & Public goods\\  
      Model:                                     & (1)              & (2)         & (3)     & (4)\\  
      \midrule
      \emph{Variables}\\
      Switch to another state                    & 0.07$^{*}$       & 0.004       & 0.02    & -0.05$^{*}$\\   
                                                 & (0.04)           & (0.03)      & (0.03)  & (0.03)\\   
      Switch to another state $\times$ Conquest  & -0.03            & -0.08$^{*}$ & -0.03   & -0.005\\   
                                                 & (0.04)           & (0.05)      & (0.04)  & (0.03)\\   
      Switch to another state $\times$ Other     & -0.03            & -0.01       & -0.04   & 0.03\\   
                                                 & (0.04)           & (0.04)      & (0.03)  & (0.03)\\   
      Switching indicator                        & 0.01             & 0.05$^{*}$  & 0.006   & -0.02\\   
                                                 & (0.03)           & (0.03)      & (0.02)  & (0.03)\\   
      \midrule
      \emph{Fixed-effects}\\
      City                                       & Yes              & Yes         & Yes     & Yes\\  
      Period                                     & Yes              & Yes         & Yes     & Yes\\  
      \midrule
      \emph{Fit statistics}\\
      Observations                               & 2,955            & 2,955       & 2,955   & 2,955\\  
      R$^2$                                      & 0.4287           & 0.4530      & 0.4802  & 0.4493\\  
      Within R$^2$                               & 0.0020           & 0.0046      & 0.0007  & 0.0017\\  
      \midrule \midrule

>>>>

\begin{table}[htbp]
   \caption{\label{tab:window_100y} Differences in trends after switching, by switch type}
   \centering
   \begin{tabular}{lcccc}
      \tabularnewline \midrule \midrule
      Dependent Variables:                       & All construction & State       & Private & Public goods\\  
      Model:                                     & (1)              & (2)         & (3)     & (4)\\  
      \midrule
      \emph{Variables}\\
      Switch to another state                    & 0.07$^{*}$       & 0.00        & 0.02    & -0.05$^{*}$\\   
                                                 & (0.04)           & (0.03)      & (0.03)  & (0.03)\\   
      Switch to another state $\times$ Conquest  & -0.03            & -0.08$^{*}$ & -0.03   & -0.01\\   
                                                 & (0.04)           & (0.05)      & (0.04)  & (0.03)\\   
      Switch to another state $\times$ Other     & -0.03            & -0.01       & -0.04   & 0.03\\   
                                                 & (0.04)           & (0.04)      & (0.03)  & (0.03)\\   
      Switching indicator                        & 0.02             & 0.05$^{*}$  & 0.01    & -0.02\\   
                                                 & (0.03)           & (0.03)      & (0.02)  & (0.02)\\   
      \midrule
      \emph{Fixed-effects}\\
      City                                       & Yes              & Yes         & Yes     & Yes\\  
      Period                                     & Yes              & Yes         & Yes     & Yes\\  
      \midrule
      \emph{Fit statistics}\\
      Observations                               & 2,955            & 2,955       & 2,955   & 2,955\\  
      R$^2$                                      & 0.4287           & 0.4530      & 0.4802  & 0.4493\\  
      Within R$^2$                               & 0.0020           & 0.0046      & 0.0007  & 0.0017\\  
      \midrule \midrule

### 2023-06-22 paper/output/regressions/window_10y.tex
#28 round results to two decimals

\begin{table}[htbp]
   \caption{\label{tab:window_10y} Differences in trends after switching, by switch type}
   \centering
   \begin{tabular}{lcccc}
      \tabularnewline \midrule \midrule
      Dependent Variables:                       & All construction & State   & Private               & Public goods\\  
      Model:                                     & (1)              & (2)     & (3)                   & (4)\\  
      \midrule
      \emph{Variables}\\
      Switch to another state                    & 0.01$^{*}$       & 0.003   & -0.004                & -0.008$^{**}$\\   
                                                 & (0.009)          & (0.004) & (0.003)               & (0.003)\\   
      Switch to another state $\times$ Conquest  & -0.008           & -0.01   & 0.003                 & 0.004\\   
                                                 & (0.01)           & (0.007) & (0.005)               & (0.005)\\   
      Switch to another state $\times$ Other     & -0.01            & -0.005  & 0.002                 & 0.01$^{**}$\\   
                                                 & (0.01)           & (0.005) & (0.004)               & (0.005)\\   
      Switching indicator                        & -0.03$^{***}$    & -0.004  & -0.005                & -0.010$^{**}$\\   
                                                 & (0.01)           & (0.005) & (0.004)               & (0.004)\\   
      \midrule
      \emph{Fixed-effects}\\
      City                                       & Yes              & Yes     & Yes                   & Yes\\  
      Period                                     & Yes              & Yes     & Yes                   & Yes\\  
      \midrule
      \emph{Fit statistics}\\
      Observations                               & 35,168           & 35,168  & 35,168                & 35,168\\  
      R$^2$                                      & 0.1770           & 0.0835  & 0.1278                & 0.0890\\  
      Within R$^2$                               & 0.0004           & 0.0001  & $8.13\times 10^{-5}$  & 0.0004\\  
      \midrule \midrule

>>>>

\begin{table}[htbp]
   \caption{\label{tab:window_10y} Differences in trends after switching, by switch type}
   \centering
   \begin{tabular}{lcccc}
      \tabularnewline \midrule \midrule
      Dependent Variables:                       & All construction & State  & Private               & Public goods\\  
      Model:                                     & (1)              & (2)    & (3)                   & (4)\\  
      \midrule
      \emph{Variables}\\
      Switch to another state                    & 0.02$^{*}$       & 0.00   & 0.00                  & -0.01$^{**}$\\   
                                                 & (0.01)           & (0.00) & (0.00)                & (0.00)\\   
      Switch to another state $\times$ Conquest  & -0.01            & -0.01  & 0.00                  & 0.00\\   
                                                 & (0.02)           & (0.01) & (0.01)                & (0.01)\\   
      Switch to another state $\times$ Other     & -0.02            & -0.01  & 0.00                  & 0.01$^{**}$\\   
                                                 & (0.01)           & (0.00) & (0.00)                & (0.00)\\   
      Switching indicator                        & -0.03$^{***}$    & 0.00   & 0.00                  & -0.01$^{**}$\\   
                                                 & (0.01)           & (0.01) & (0.00)                & (0.00)\\   
      \midrule
      \emph{Fixed-effects}\\
      City                                       & Yes              & Yes    & Yes                   & Yes\\  
      Period                                     & Yes              & Yes    & Yes                   & Yes\\  
      \midrule
      \emph{Fit statistics}\\
      Observations                               & 35,168           & 35,168 & 35,168                & 35,168\\  
      R$^2$                                      & 0.1770           & 0.0835 & 0.1278                & 0.0890\\  
      Within R$^2$                               & 0.0004           & 0.0001 & $8.13\times 10^{-5}$  & 0.0004\\  
      \midrule \midrule

### 2023-06-22 paper/output/regressions/window_50y.tex
#28 round results to two decimals

\begin{table}[htbp]
   \caption{\label{tab:window_50y} Differences in trends after switching, by switch type}
   \centering
   \begin{tabular}{lcccc}
      \tabularnewline \midrule \midrule
      Dependent Variables:                       & All construction & State         & Private & Public goods\\  
      Model:                                     & (1)              & (2)           & (3)     & (4)\\  
      \midrule
      \emph{Variables}\\
      Switch to another state                    & 0.02             & 0.02          & 0.002   & -0.04$^{***}$\\   
                                                 & (0.02)           & (0.02)        & (0.01)  & (0.01)\\   
      Switch to another state $\times$ Conquest  & 0.04             & -0.07$^{***}$ & -0.005  & 0.02\\   
                                                 & (0.04)           & (0.03)        & (0.02)  & (0.02)\\   
      Switch to another state $\times$ Other     & 0.008            & -0.02         & 0.006   & 0.04$^{**}$\\   
                                                 & (0.03)           & (0.02)        & (0.01)  & (0.02)\\   
      Switching indicator                        & -0.01            & 0.007         & -0.005  & 0.0006\\   
                                                 & (0.02)           & (0.02)        & (0.01)  & (0.01)\\   
      \midrule
      \emph{Fixed-effects}\\
      City                                       & Yes              & Yes           & Yes     & Yes\\  
      Period                                     & Yes              & Yes           & Yes     & Yes\\  
      \midrule
      \emph{Fit statistics}\\
      Observations                               & 6,635            & 6,635         & 6,635   & 6,635\\  
      R$^2$                                      & 0.3553           & 0.2798        & 0.3257  & 0.2917\\  
      Within R$^2$                               & 0.0009           & 0.0012        & 0.0002  & 0.0011\\  
      \midrule \midrule

>>>>

\begin{table}[htbp]
   \caption{\label{tab:window_50y} Differences in trends after switching, by switch type}
   \centering
   \begin{tabular}{lcccc}
      \tabularnewline \midrule \midrule
      Dependent Variables:                       & All construction & State         & Private & Public goods\\  
      Model:                                     & (1)              & (2)           & (3)     & (4)\\  
      \midrule
      \emph{Variables}\\
      Switch to another state                    & 0.02             & 0.02          & 0.00    & -0.04$^{***}$\\   
                                                 & (0.02)           & (0.02)        & (0.01)  & (0.01)\\   
      Switch to another state $\times$ Conquest  & 0.04             & -0.07$^{***}$ & 0.00    & 0.02\\   
                                                 & (0.04)           & (0.03)        & (0.02)  & (0.02)\\   
      Switch to another state $\times$ Other     & 0.01             & -0.02         & 0.01    & 0.04$^{**}$\\   
                                                 & (0.03)           & (0.02)        & (0.01)  & (0.02)\\   
      Switching indicator                        & -0.01            & 0.01          & -0.01   & 0.00\\   
                                                 & (0.02)           & (0.02)        & (0.01)  & (0.01)\\   
      \midrule
      \emph{Fixed-effects}\\
      City                                       & Yes              & Yes           & Yes     & Yes\\  
      Period                                     & Yes              & Yes           & Yes     & Yes\\  
      \midrule
      \emph{Fit statistics}\\
      Observations                               & 6,635            & 6,635         & 6,635   & 6,635\\  
      R$^2$                                      & 0.3553           & 0.2798        & 0.3257  & 0.2917\\  
      Within R$^2$                               & 0.0009           & 0.0012        & 0.0002  & 0.0011\\  
      \midrule \midrule
